cardinalR: Generating interesting high-dimensional data structures

### 2025-06-24 paper-cardinalR.Rmd
Put code and acknowlegement together

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     #aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "bottom", 
     legend.title = element_blank(), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm'),
     plot.margin = margin(0, 0, 0, 0)
   )
)
```

@@

nonlinear_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

nonlinear_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

nonlinear_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

# Code

The code is available at [https://github.com/JayaniLakshika/cardinalR](https://github.com/JayaniLakshika/cardinalR), and source material for this paper is available at [https://github.com/JayaniLakshika/paper-cardinalR](https://github.com/JayaniLakshika/paper-cardinalR).

@@

>>>>

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "bottom", 
     legend.title = element_blank(), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm'),
     plot.margin = margin(0, 0, 0, 0)
   )
)
```

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.3, 
                                              axis_pos_y = -0.3, 
                                              threshold = 0.022))

nonlinear_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.45, 0.73), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.45,
                                              axis_scaled = 1.3, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.01))

nonlinear_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.3, 0.43), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.5,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.016))

nonlinear_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.35, 0.4), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

@@

The package is available at [https://github.com/JayaniLakshika/cardinalR](https://github.com/JayaniLakshika/cardinalR), and source material for this paper is available at [https://github.com/JayaniLakshika/paper-cardinalR](https://github.com/JayaniLakshika/paper-cardinalR).

### 2025-06-24 paper-cardinalR.tex
Put code and acknowlegement together

\section{Code}\label{code}

The code is available at \url{https://github.com/JayaniLakshika/cardinalR}, and source material for this paper is available at \url{https://github.com/JayaniLakshika/paper-cardinalR}.

@@

>>>>

@@

The package is available at \url{https://github.com/JayaniLakshika/cardinalR}, and source material for this paper is available at \url{https://github.com/JayaniLakshika/paper-cardinalR}.
